\documentclass{resume}
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Héctor Eduardo Garza Fraga}
\address{
    +52 81 1299 5975 \ $\cdot$ \ Monterrey, MX \ $\cdot$ \ \href{mailto:garzahector1013@gmail.com}{garzahector1013@gmail.com}
}
\address{
    \href{https://www.linkedin.com/in/osifraga/}{LinkedIn} \ $\cdot$ \ 
    \href{https://github.com/Fraga9}{GitHub} \ $\cdot$ \ 
    \href{https://osifraga.dev/}{Portfolio}
}
\begin{document}

\begin{rSection}{Education}
{\bf B. S. Computer Science and Technology}, Tecnológico de Monterrey \hfill {Aug 2022 - June 2026 (Expected)}\\
\textit{Concentration in Advanced Artificial Intelligence for Data Science}\\
{\bf Honors \& Achievements:} 100\% Academic Merit Scholarship, Xignux Challenge 2024, Top 3 Finalist
\end{rSection}

\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Python, JavaScript, C++, SQL, Java\\
AI / ML & Tensorflow, PyTorch, LangChain, Gemini API\\
Frameworks & React, Next.js, FastAPI, React Native, Flask, Svelte, Astro \\
Tools & Supabase, GitHub, AWS, Google Firebase, OCI, Jupyter Notebook
\end{tabular}
\end{rSection}

\begin{rSection}{Experience}
\textbf{Full Stack Developer Intern, Cemex} \hfill {Feb 2025 - Present} \\
{\small Next.js, FastAPI, PostgreSQL, Supabase, LangChain, Mapbox, Python}
\begin{itemize}
    \item Architected MOV, a full-scale fleet intelligence platform managing 282 vehicles across 60+ branches: vehicle registry, maintenance tracking, fuel transaction management, real-time GPS dashboards, automated anomaly detection, and role-based access control.
    \item Engineered intelligent fuel theft detection using statistical anomaly analysis over consumption patterns, and continuous speed violation monitoring with per-vehicle thresholds (80/120 km/h) enforced over live GPS streams.
    \item Built an LLM-driven SQL agent enabling natural-language queries over fleet operations data, reducing ad-hoc reporting turnaround from hours to seconds.
\end{itemize}
\textbf{AI Engineer Intern, Infosys (InStep)} {AI Agents, Semantic Search, LLM, Python, React}\hfill {Jun 2024 - Aug 2024}
\begin{itemize}
    \item Developed a semantic caching system integrated with EdgeVerve chatbot for PDF data retrieval, reducing process time by 90\%.
    \item Engineered a multi-agent orchestration system enabling dynamic task creation with personalized dashboards, deployed for internal teams at Infosys EdgeVerve.
\end{itemize}
\end{rSection}

\begin{rSection}{Projects}

% --- SMARTCOLONIA ---
\textbf{SmartColonia: Neighborhood Mgmt. Platform} {FastAPI, React Native, AWS S3} \hfill 
\begin{itemize}
    \item Developed a SaaS application with three user levels (Security Guard, Resident, Administrator) in beta with 200 users, projecting 1,000 users within six months.
    \item Implemented access control modules, integrated payment system, community announcements, and survey tools for neighborhood management.
\end{itemize}

% --- VIBEMATCH ---
\textbf{VibeMatch: AI Music Compatibility} {Next.js 15, FastAPI, PyTorch, Qdrant} \hfill \href{https://www.vibematchs.me/}{Website}
\begin{itemize}
    \item Engineered a recommendation engine using Graph Neural Networks (LightGCN) to analyze 338K+ tracks and 6.9K artists, achieving 1.00 Precision and 0.64 Recall@10.
    \item Architected a real-time vector search system with Qdrant and FastAPI, reducing query latency to 10ms and optimizing end-to-end processing to 800ms.
\end{itemize}

% --- TOPOGRAFIA ---
\textbf{Topografía Cemex: Mgmt. System} {React, FastAPI, PostgreSQL, Supabase} \hfill \href{https://topografia-two.vercel.app/}{Demo}
\begin{itemize}
    \item Developed a road construction QC system with real-time data capture and automatic SCT compliance validation.
    \item Automated elevation calculations using PostgreSQL triggers and TanStack Query for optimized reporting.
\end{itemize}

\end{rSection}

\end{document}
